強化学習モデル: 最尤推定

### 2021-05-21 how-to-cognitive-modeling-rl1.Rmd
update

```{r}
method <- c("grid", "optim", "pso")
alpha <- c(result_grid$calc_results$store_alpha[maxIndex],result_optim$par[1],result_pso$par[1])
beta <- c(result_grid$calc_results$store_beta[maxIndex],result_optim$par[2],result_pso$par[1])
loglikelihood <- c(result_grid$calc_results$store_loglike[maxIndex],-result_optim$value,-result_pso$value)

>>>>

```{r}
method <- c("grid", "optim", "pso")
alpha <- c(result_grid$calc_results$store_alpha[maxIndex],result_optim$par[1],result_pso$par[1])
beta <- c(result_grid$calc_results$store_beta[maxIndex],result_optim$par[2],result_pso$par[2])
loglikelihood <- c(result_grid$calc_results$store_loglike[maxIndex],-result_optim$value,-result_pso$value)
